{\sectionstyle{Work Experience}}
\newline{}
\employerandlocation{New Zealand Government}{Blenheim, New Zealand}
\positionanddates{Solutions Architect}{January 2023 $-$ Present}
\bulletedlist{%
        \item{} {Enterprise technical lead for cloud and compute platforms, developer tooling and automation.}
        \item{} {Responsible for the creation, communication, prioritisation and integration of architecture strategy and roadmaps.}
        \item{} {Designed and implemented highly{-}available, multi{-}organisation, on{-}premises Kubernetes cluster, resulting in reduced
               \\platform costs, automated security control implementation, and increased organisational agility.}
        \item{} {Set standards for, and led organisational adoption of, DevOps and GitOps practices for both public cloud and
               \\on{-}premises platforms, systems and applications.}
        \item{} {Represent New Zealand in ongoing international engagements and technical forums, contributing to global standards
               \\in a way that forwards NZ values.}
}
\vspace{1mm}
\positionanddates{Senior Network Engineer}{November 2019 $-$ January 2023}
\bulletedlist{%
        \item{} {Technical lead for Azure based multi{-}organisation private cloud delivery and migration, onboarding multiple
               \\organisations and reducing their infrastructure provisioning time from weeks to minutes.}
        \item{} {Provided technical leadership and expertise to large and/or complex projects, including VXLAN/EVPN
               \\data center migration and network monitoring, logging and management systems refresh.}
        \item{} {Developed configuration management (infrastructure as code) code and tools, and pioneered adoption throughout the organisation.}
        \item{} {Definition and documentation of architecture and protocol standards.}
}
\vspace{1mm}
\positionanddates{Network Engineer}{July 2017 $-$ October 2019}
\bulletedlist{%
        \item{} {Responsible for maintenance, monitoring and troubleshooting of all network equipment.}
        \item{} {Wrote and lead internal technical training courses on the topics of networking, automation and Linux.}
        \item{} {Designed, tested and automated data center network integration for OpenStack based private cloud deployment.}
        \item{} {Provided network and systems engineering expertise towards successful delivery of a multi{-}million dollar
               \\all{-}of{-}government IT project.}
}
\vspace{2mm}
\employerandlocation{2degrees Enterprise}{Christchurch, New Zealand}
\positionanddates{Senior Managed Services Engineer}{October 2016 $-$ June 2017}
\bulletedlist{%
        \item{} {Escalation point for difficult technical queries or ongoing issues from other team members.}
        \item{} {Provided design assistance and expertise for other internal teams.}
        \item{} {Technical assessment and delegation of incoming tickets to team members.}
        \item{} {Mentored and wrote technical training for new engineers.}
}
\vspace{1mm}
\positionanddates{Managed Services Engineer}{March 2014 $-$ September 2016}
\bulletedlist{%
        \item{} {Designed, implemented and supported all services; including customised managed LAN, WAN and internet solutions.}
        \item{} {Wrote and maintained technical documentation for both internal and external use.}
}
\vspace{2mm}
\employerandlocation{Snap Internet}{Christchurch, New Zealand}
\positionanddates{Service Center Technician}{April 2013 $-$ February 2014}
\bulletedlist{%
        \item{} {Provided technical, provisioning and billing assistance for Snap Internet's residential and small business customer base.}
        \item{} {Trained new technical staff in current and new technologies.}
}
